README.md

### 2020-06-06 README.Rmd
updated readme

@@

* [The database file itself is `.csv` format](https://github.com/efernandezpascual/sylvanseeds/blob/master/results/Supplementary%20material%206%20-%20Database.csv)
* [The Sylvan Seeds `shiny` app for visualizing the database](https://sylvanseeds.shinyapps.io/sylvanseeds/)
* The article describing the collection and fields of the database, which is in preparation.

>>>>

![Sylvan Seeds](data/2017070313 Blue Ridge Parkway small.jpg)

@@

* [The database file itself is `.csv` format](https://github.com/efernandezpascual/sylvanseeds/blob/master/results/Supplementary%20material%206%20-%20Database.csv)
* [The Sylvan Seeds `shiny` app for visualizing the database](https://sylvanseeds.shinyapps.io/sylvanseeds/)
* [The article describing the collection and fields of the database](https://github.com/efernandezpascual/sylvanseeds/blob/master/doc/last/last.md), which is in preparation.

## Citation

Please cite the database as `CITATION`
